\newarray\Education
\newarray\EducationHideOnResume


\EducationHideOnResume(1)=t
\Education(1)={%
  \entry{Josef-Dering-Grundschule}{Until 2007}{}{Eichenau}{%
    \ifCV
      Elementary/primary school
    \fi
  }
}

\EducationHideOnResume(2)=t
\Education(2)={%
  \entry{Obermenzinger Gymnasium}{2007 --- 2015}{Allgemeine Hochschulreife (Higher Education Entrance Qualification)}{Munich}{%
    \ifCV
      Grade: 2.1

      The Obermenzinger Gymnasium M{\"u}nchen is a state-approved economic and social science grammar school.
    \fi
    \begin{itemize}[noitemsep, nosep]
      \item I completed various additional computer science-related courses and activities.
      \item I held a weekly programming tutorial for other pupils.
    \end{itemize}
  }
}

\Education(3)={%
  \entry{Technical University Munich}{2015 --- 2019}{Bachelor of Science (B.Sc.), Informatics: Games Engineering}{Garching}{%
    \ifCV
      Grade: 2.4

      The \enquote{Informatics: Games Engineering} bachelor's degree at TUM is a technically-oriented program for students interested in game development. Games production is a booming industry that is set to grow rapidly in the near future. This new technology is utilized in many industries, including engineering, construction, medicine, and education.
    \fi

    \begin{itemize}[noitemsep, nosep]
      \item Focused on Virtual Reality and Machine Learning in the field of Human-computer interaction (HCI)
      \item Wrote my bachelor's thesis about using smartphones to interact with Virtual Reality (graded 1.0/A+)
    \end{itemize}
  }
}

\Education(4)={%
  \entry{Technical University Munich}{2019 --- 2022}{Master of Science (M.Sc.), Informatics}{Garching}{%
    \ifCV
      Grade: 1.6

      The Department of Informatics at TUM is one of the largest and most renowned computer science departments in Germany, and the professors and teaching staff are experts in their respective fields. Students of the master's programs receive a top-level education and can tailor their program to focus in-depth on the topics that interest them most.
    \fi

    \begin{itemize}[noitemsep, nosep]
      \item Focused on Internet of Things and Cloud Computing
      \item In my master's thesis, I presented a novel IaC approach to formulate platform-independent cloud architectures and a transpiler system to deploy to different cloud platforms without platform-specific knowledge (graded 1.0/A+)
    \end{itemize}
  }
}
